Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-22 01_Meta-analysis_experiments.Rmd
Added in the whole rating system in instead of the reference to the incomplete paper

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale and can be read in the
file "Powdery mildew paper#1.doc".  
Comparing trials which have not used the same rating scale will be done using a
percentage change.

>>>>

**2001 - 2004 trials**  
Trial data were obtained from a non-published manuscript.  
Ratings for powdery mildew were on a 1-5 rating scale where 1 = no sign of disease, 2 = 1-30% diseased leaf area, 3 = 31-65% diseased leaf area, 4 = 66-99% diseased leaf area and 5 = complete defoliation.  
Comparing trials which have not used the same rating scale will be done using a
percentage change.
